Peer Assignment 1
========================================================
Loading and preprocessing the data
```{r, echo = TRUE}
data <- read.csv("activity.csv")
data <- data.frame(data)
```

Histogram of the total number of steps taken each day

```{r, echo = TRUE}
DataNoNA <- data[complete.cases(data),]
DataNoNA[,2] <- as.character(DataNoNA[,2])
stepsD <- tapply(DataNoNA$steps,DataNoNA$date,sum)
barplot(stepsD,xlab="date",ylab="steps",main="Total Number of Steps per Day")
```

Calculate and report the mean and median total number of steps taken per day
```{r, echo = TRUE}
mean(stepsD)
median(stepsD)
```

A time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r, echo = TRUE}
stepsI <- tapply(DataNoNA$steps,DataNoNA$interval,mean)
plot(names(stepsI),stepsI,type="l",xlab="interval",ylab="mean of steps",main="Average Number of Steps")
```

Which 5-minute interval,average across all the days in the dataset, contains the maximum number of steps?
```{r, echo = TRUE}
names(stepsI[stepsI==max(stepsI)])
```

Imputing missing values
```{r, echo = TRUE}
nrow(data)-sum(complete.cases(data))

NewData <- data
for (i in (1:nrow(data))[!complete.cases(data)]){
        NewData[i,1]<-stepsI[names(stepsI)==NewData[i,3]]
}
```

Calculate total number of steps per day with new dataset
```{r, echo = TRUE}
stepsD2 <- tapply(NewData$steps,NewData$date,sum)
barplot(stepsD,xlab="date",ylab="steps",main="Total Number of Steps per Day")
```

Mean and median
```{r, echo = TRUE}
mean(stepsD2)
median(stepsD2)
```
After imputing missing values,median has been the same as the mean

Make a panel plot containing a time series plot with new factor variable
```{r, echo = TRUE}
NewData[,2] <- as.Date(NewData[,2])
Weekdays<-weekdays(NewData[,2])

WeekendData <- NewData[Weekdays==c("Saturday","Sunday"),]
WeekdayData <- NewData[!Weekdays==c("Saturday","Sunday"),]

stepsIinWend <- tapply(WeekendData$steps,WeekendData$interval,mean)
stepsIinDay <- tapply(WeekdayData$steps,WeekdayData$interval,mean)

stepsEnd <- cbind(names(stepsIinWend),as.character(stepsIinWend),rep("weekend",length(stepsIinWend)))
stepsDay <- cbind(names(stepsIinDay),as.character(stepsIinDay),rep("weekday",length(stepsIinDay)))


stepsW <- rbind(stepsEnd,stepsDay)
stepsW <- data.frame(stepsW)
stepsW[,1] <- as.numeric(as.character(stepsW[,1]))
stepsW[,2] <- as.character(stepsW[,2])
stepsW[,2] <- as.numeric(stepsW[,2])
names(stepsW) <- c("interval","steps","week")


library(lattice)
xyplot(steps~interval|week,layout=c(1,2),data=stepsW,type="l",ylab="Numbers of steps",xlab="Interval")
```

The End

